---
title: "ResultsV4"
author: "Hassan"
date: "5/24/2021"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```


```{r, warning=FALSE, include=FALSE}
library('reshape2')
library('tidyr')
library('car')
library('lsr')
library('jtools')
library('sciplot')
library('ggplot2')
library('ggsignif')
library('rcompanion')

```

```{r}
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- plyr::rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```



```{r}
allPairsDistance_all<-read.csv("C://Users//al33m//Box//Grzywacz Lab//Experiment//age_DataFiles//Rfiles//AllPairsDistance_all.csv")
allPairsDistance_all$Subnum<-as.factor(allPairsDistance_all$Subnum)
allPairsDistance_all$Subname<-factor(allPairsDistance_all$Subname)
allPairsDistance_all$subSortAF<-as.factor(allPairsDistance_all$subSortAF)
allPairsDistance_all$Gender<-factor(allPairsDistance_all$Gender)
allPairsDistance_all$Category<-factor(allPairsDistance_all$Category)
allPairsDistance_all$Timepoint<-factor(allPairsDistance_all$Timepoint)
allPairsDistance_all$changed<-factor(allPairsDistance_all$changed)
allPairsDistance_all$adaptiveCut<-lsr::quantileCut(allPairsDistance_all$Age,6)


allPairsDistance_AF<-read.csv("C://Users//al33m//Box//Grzywacz Lab//Experiment//age_DataFiles//Rfiles//AllPairsDistance_AF.csv")
allPairsDistance_AF$Subnum<-as.factor(allPairsDistance_AF$Subnum)
allPairsDistance_AF$subSortAF<-as.factor(allPairsDistance_AF$subSortAF)
allPairsDistance_AF$Subname<-factor(allPairsDistance_AF$Subname)
allPairsDistance_AF$Gender<-factor(allPairsDistance_AF$Gender)
allPairsDistance_AF$Category<-factor(allPairsDistance_AF$Category)
allPairsDistance_AF$Timepoint<-factor(allPairsDistance_AF$Timepoint)
allPairsDistance_AF$changed<-factor(allPairsDistance_AF$changed)
allPairsDistance_AF$adaptiveCut<-lsr::quantileCut(allPairsDistance_AF$Age,6)
allPairsDistance_AF$GAD<-as.numeric(allPairsDistance_AF$GAD)
allPairsDistance_AF$rGtps<-as.numeric(allPairsDistance_AF$rGtps)

bis<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\ForR\\SCP\\CSV\\BISResults.csv")

allPairsTogether<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\ForR\\SCP\\CSV\\newAllPairsTogether.csv")
cols<-c('timepoint','subname','Limg','Rimg','Lint','Rint','pair','category','class','subnum','subSortAF','change','diff', 'OrankDiff')
allPairsTogether[cols]<-lapply(allPairsTogether[cols],factor)

allPairsTogetherAF<-allPairsTogether%>%dplyr::filter(class=='Fixed')

allCountsSummary<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\ForR\\SCP\\CSV\\allCountsSummary.csv")
cols <- c('subnum','category','hue')
allCountsSummary[cols]<-lapply(allCountsSummary[cols],factor)
allCountsSummary$meanValenceSqrd<-allCountsSummary$meanValence^2
allCountsSummary$fixed_diff<-(allCountsSummary$fixed_diff*5)/70


typDF<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\age_DataFiles\\Rfiles\\typDF.csv")

#drop sub 96

allPairsDistance_AF<-allPairsDistance_AF%>%dplyr::filter(subSortAF!=96)
allPairsDistance_all<-allPairsDistance_all%>%dplyr::filter(subSortAF!=96)
bis<-bis%>%dplyr::filter(subnum!=84)
allPairsTogether<-allPairsTogether%>%dplyr::filter(subSortAF!=96)
allCountsSummary<-allCountsSummary%>%dplyr::filter(subSortAF!=96)

bis<-bis%>%dplyr::filter(!subnum %in% c(16,20,31,42,45,60,64,73,75,79))


twoBody<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\ForR\\twoBody.csv")
twoBody$Type<-factor(twoBody$Type,levels=c('Unchanged','Changed'))
twoBody$Timepoint<-factor(twoBody$Timepoint, levels=c('20min','1wk','2wks','3wks','4wks'))

overallTriadDF<-read.csv("C:\\Users\\al33m\\Box\\Grzywacz Lab\\Experiment\\ForR\\SCP\\CSV\\overallTriadDF.csv")#filtered for chance
cols<-c('category','timept','subname','subnum','change','markers','subSortAF')
overallTriadDF[cols]<-lapply(overallTriadDF[cols],factor)

# subSortSummary_cat_AF<-summarySE(allPairsDistance_AF,measurevar = 'Instability',groupvars = c('subSortAF','Category'))
# summary.changed<-summarySE(allPairsTogether,measurevar='value',groupvars=c('subSortAF','change'))
# summary.class<-summarySE(allPairsTogether,measurevar='value',groupvars=c('subSortAF','class'))


chanceSubs<-c(55,59,72,80,88,91,92,93,94,95)


allPairsDistance_AF$newSubSortAF<-plyr::mapvalues(allPairsDistance_AF$subSortAF,from = sort(unique(allPairsDistance_AF$subSortAF)), to = 1:85)
allPairsDistance_all$newSubSortAF<-plyr::mapvalues(allPairsDistance_all$subSortAF,from = sort(unique(allPairsDistance_all$subSortAF)), to = 1:85)
allPairsTogether$newSubSortAF<-plyr::mapvalues(allPairsTogether$subSortAF,from = sort(unique(allPairsTogether$subSortAF)), to = 1:85)

setdiff(sort(unique(allPairsDistance_AF$subSortAF)),sort(unique(allCountsSummary$subSortAF)))
#subjects 26 and 66 didn't partake in the all counts
# allCountsSummary$newSubSortAF<-mapvalues(allCountsSummary$subSortAF,from = sort(unique(allCountsSummary$subSortAF)), to = 1:83)

```
# Illustrative Subjects


```{r threeBody, fig.width=18, fig.asp=0.3, fig.align = 'center', fig.cap ='An illustration of the differences in aesthetic-preference instability across subjects. Index of Preference Change Relative to Session 1A for the two illustrative subjects.  The horizontal axis represents time elapsed, corresponding with the radar plots above and the asterisks indicate that the change in preference is statistically significant.'}

ggplot(twoBody,
       aes(x=Timepoint,y=Instability,fill=Type))+
      geom_bar(stat='identity',position=position_dodge(),color='black')+

          theme(
    # Remove panel border
    panel.border = element_blank(),  
    # Remove panel grid lines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # Remove panel background
    panel.background = element_blank(),
    # Add axis line
    axis.line = element_line(colour = "black",size=2),
    axis.ticks.length =unit(.25,'cm') )+
scale_fill_hue(c=45, l=80)+
  ylab('Index of Preference Change')+
  theme(text = element_text(size=24))+
  theme(legend.position='bottom')

```




# Individual Differences in Preference Instability

```{r}

model<-lm(Instability~Subname,allPairsDistance_AF)
sstable<-car::Anova(model, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model)$fstatistic[1])
df_model <- unname(summary(model)$fstatistic[2])
df_res <- unname(summary(model)$fstatistic[3])
rsq <- summary(model)$r.squared
p <- pf(fstat, df_model, df_res, lower.tail = FALSE)
```

$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$. 

# All Subjects  x Categories

```{r indivdiffs, fig.width=12, fig.asp=0.7, fig.align = 'center', fig.cap='Mean Index of Preference Change relative to Session 1A, colored by object category.  Subjects are numbered in order of increasing mean index, with the error bars indicating standard errors (all error bars in this article are standard errors).  The dotted line represents the index of a subject choosing at random.  Thus, almost all participants are significantly more stable than chance.  We can also see that instability is highly individual, that is, the difference of instability between the most and least stable subjects is significant.   The statistical analysis in the text reveals that phones and shirts are overall more unstable than cars.  However, the graph shows that, for some individuals, cars are the most unstable.  Not only that, all six possible orders of rankings of categories can be observed across the subjects.'}


everysecond <- function(x){
x <- sort(unique(x))
x[seq(2, length(x), 2)] <- ""
x
}


subSortSummary_cat_AF<-summarySE(allPairsDistance_AF,measurevar = 'Instability',groupvars = c('newSubSortAF','Category'))

subSortSummary_cat_AF %>%
    ggplot(aes(x=newSubSortAF,y=Instability, color=Category))+
    geom_point(size=3)+
    geom_errorbar(aes(ymin=Instability-se, ymax=Instability+se),size=1, width=.01)+
    ylim(0,0.55)+
    geom_hline(yintercept=0.46, linetype="dashed", color = "black", size=0.7)+
    labs(x='Subject #',y='Instability')+
    theme(
    # Remove panel border
    panel.border = element_blank(),  
    # Remove panel grid lines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # Remove panel background
    panel.background = element_blank(),
    # Add axis line
    axis.line = element_line(colour = "black",size=2),
    axis.ticks.length=unit(.25, "cm"))+
    scale_color_discrete(name='Category',
                          labels = c("Car",'Phone','Shirt'))+
  theme(text = element_text(size=14))+
  scale_x_discrete(labels = everysecond(1:85))+
  ylab('Index of Preference Change')



```

# Categories Only
```{r, catDiff, fig.width=12, fig.asp=0.7, fig.align = 'center', fig.cap='Category wise comparison in regards to mean instability. The graph shows that Cars were the most stable, while phones and shirts were equal'}
ggplot(allPairsDistance_AF,
       aes(x=Category,y=Instability, color=Category))+
  stat_summary(fun='mean',geom='point')+
  stat_summary(fun.data='mean_se',geom='errorbar',width=0.1)+
     labs(y=' Instability',x='Category ')+
                theme(
              # Remove panel border
              panel.border = element_blank(),  
              # Remove panel grid lines
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              # Remove panel background
              panel.background = element_blank(),
              # Add axis line
              axis.line = element_line(colour = "black"))+
  
  scale_x_discrete(labels=c('Cars','Phones Cases','Shirts'))+
  scale_color_discrete(name="Category", 
                       labels=c('Cars','Phones','Shirts'))+
      theme(text = element_text(size=12))

```

ANOVA
```{r}
model_category<-lm(Instability~Category,allPairsDistance_AF)
sstable<-car::Anova(model_category, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_category)$fstatistic[1])
df_model_category <- unname(summary(model_category)$fstatistic[2])
df_res <- unname(summary(model_category)$fstatistic[3])
rsq <- summary(model_category)$r.squared
p <- pf(fstat, df_model_category, df_res, lower.tail = FALSE)
```

 $R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$. 
 
 

Post Hoc Tukey
```{r}
TukeyHSD(aov(Instability~Category,allPairsDistance_AF))
```

Is there a  Category and Subject interaction?
```{r}
model_category<-lm(Instability~Category*subSortAF,allPairsDistance_AF)
sstable<-car::Anova(model_category, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_category)$fstatistic[1])
df_model_category <- unname(summary(model_category)$fstatistic[2])
df_res <- unname(summary(model_category)$fstatistic[3])
rsq <- summary(model_category)$r.squared
p <- pf(fstat, df_model_category, df_res, lower.tail = FALSE)
```

 $R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$. 

There appears to be an intreaction.However, not a clear one.

# Instability Relative To The First Session
```{r}
model_AF<-lm(Instability~Timepoint,allPairsDistance_all)
sstable<-car::Anova(model_AF, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_AF)$fstatistic[1])
df_model_AF <- unname(summary(model_AF)$fstatistic[2])
df_res <- unname(summary(model_AF)$fstatistic[3])
rsq <- summary(model_AF)$r.squared
p <- pf(fstat, df_model_AF, df_res, lower.tail = FALSE)
```

$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$. 

Tukey HSD
```{r}
TukeyHSD(aov(Instability~Timepoint,allPairsDistance_AF))

```




# Instability Relative To All Sessions 

```{r allSessions, fig.width = 12, fig.asp = 0.7, fig.align = 'center', fig.cap='Subject Index of Preference Change Relative to a Fixed Earlier Session.  The vertical axis represents mean overall index across subjects.  The five different curves represent different reference sessions, colored as shown in the legend.  The horizontal axis represents time elapsed relative to the starting point of each session. In general, the index of preference change increases as a function of time after the reference session, plateauing after long delays.  Furthermore, this index decreases as the reference session increases and subjects complete more sessions, suggesting a stabilizing effect of making a choice.'}

sum.timept.instability<-summarySE(allPairsDistance_all,measurevar = "Instability", groupvars = (c("Timepoint")))

sum.timept.instability$group<-c(rep(c('Session 1'),5),rep(c('Session 2'),4),rep(c('Session 3'),3),rep(c('Session 4'),2),rep(c('Session 5'),1))
sum.timept.instability$group<-factor(sum.timept.instability$group, levels=c('Session 1', 'Session 2','Session 3','Session 4','Session 5'))

sum.timept.instability$timeElap<-as.factor(c('20min', '1 wk','2 wks','3 wks','4 wks', '1 wk','2 wks','3 wks','4 wks','1 wk','2 wks','3 wks','1 wk','2 wks','1 wk'))
sum.timept.instability$timeElap<-factor(sum.timept.instability$timeElap, levels=c('20min', '1 wk','2 wks','3 wks','4 wks'))
mylabs<-c('20min', '1 wk','2 wks','3 wks','4 wks', '1 wk','2 wks','3 wks','4 wks','1 wk','2 wks','3 wks','1 wk','2 wks','1 wk')


ggplot(sum.timept.instability,aes(x=Timepoint,y=Instability,group=group,color=group))+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=Instability-se, ymax=Instability+se), size=1, width=.1)+
  geom_line(size=1)+
  xlab('Time Elapsed')+
  ylab('Index of Preference Change')+
  scale_color_discrete(name="Reference Session", 
                       labels=c('Session 1A','Session 1B','Session 2','Session 3', 'Session 4'))+
  ylim(0.175,0.25)+
                theme(
              # Remove panel border
              panel.border = element_blank(),  
              # Remove panel grid lines
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              # Remove panel background
              panel.background = element_blank(),
              # Add axis line
              axis.line = element_line(colour = "black",size=2),
              axis.ticks.length=unit(.25, "cm"))+
  scale_x_discrete(labels=mylabs)+
    theme(text = element_text(size=14))



```



# Comparing Instability Relative To First Session vs Consecutive Sessions
```{r, fig.width=18, fig.asp=0.5, fig.align = 'center', fig.cap='Evidence that choice stabilizes aesthetic preference.  (A) Index of Preference Change for each subject as a measured relative to Session 1A (blue) or relative to the preceding session (red).  Lower indices in the latter suggest that the subject was updating preferences concordantly after each session.  Asterisks represent a statistically significant difference between the mean indices at preceding sessions compared to Session 1A, as measured by a proportion z test.  A total of 17 subjects passed this test.  We refer to these subjects as “Constructed” because their later choices are constructed upon the earlier ones (a term borrowed from the economics literature).'}

summary.class<-summarySE(allPairsTogether,measurevar='value',groupvars=c('newSubSortAF','class'))

ggplot(summary.class,
       aes(x=newSubSortAF,y=value,color=class))+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=value-se, ymax=value+se), size=1, width=.1)+ylim(0,0.5)+
  labs(x='Subject #',y='Index of Preference Change')+
theme(
# Remove panel border
panel.border = element_blank(),  
# Remove panel grid lines
panel.grid.major = element_blank(),
panel.grid.minor = element_blank(),
# Remove panel background
panel.background = element_blank(),
# Add axis line
axis.line = element_line(colour = "black",size=2),
axis.ticks.length=unit(.25, "cm"))+
    theme(text = element_text(size=14))+
  scale_x_discrete(labels = everysecond(1:85))+
 scale_color_discrete(name='',
                          labels = c("Relative to Preceding Session",'Relative to Session 1A'))
```



# Comparing Subjects Who 'constructed' Their Preferences To Those Who Did Not
```{r, fig.width=18, fig.asp=0.5, fig.align = 'center', fig.cap='(B) Subject Index of Preference Change relative to the preceding session, separating Constructed (blue) and Other (red) subjects in two groups.  The horizontal axis represents consecutive sessions being compared. While the blue line falls, the red line does not.  The diverging lines indicate that Constructed subjects, but not the others, tend to update their preferences from one session to the next one.'}

mylabs<-c('1A-1B','1B-2','2-3','3-4','4-5')

ggplot(summarySE(allPairsTogether%>%dplyr::filter(class=='Consecutive'),'value',c('timepoint','change')),
       aes(x=timepoint,y=value,color=change,group=change))+
  stat_summary(fun='mean',geom='point',size=3)+
  geom_errorbar(aes(ymin=value-se, ymax=value+se), size=1,width=.1)+
    geom_line(size=2)+
  labs(x='Session Comparison',y='Index of Preference Change')+
    scale_x_discrete(labels=mylabs)+
        scale_color_hue(labels = c("Other", "Constructed"))+
    guides(color=guide_legend("Instability Behavior"))+

  theme(
# Remove panel border
panel.border = element_blank(),  
# Remove panel grid lines
panel.grid.major = element_blank(),
panel.grid.minor = element_blank(),
# Remove panel background
panel.background = element_blank(),
# Add axis line
axis.line = element_line(colour = "black", size=2),
axis.ticks.length=unit(.25, "cm"))+
    theme(text = element_text(size=14))


```


# Differences In Instability As a Function of Hue Distance 

```{r huediff, fig.width = 18, fig.asp = 0.5, fig.align = 'center', fig.cap = 'Instability as a function of object hue difference. The x-axis represent the difference (distance) in hues on a given trial.'}
ggplot(allPairsTogether%>%dplyr::filter(class=='Fixed'),aes(x=diff,y=value))+
  stat_summary(fun = "mean", geom = "point",size=6)+
  stat_summary(fun.data = "mean_se", geom = "errorbar",size=2,width=0.1)+
  xlab('Distance Between Hues')+ ylab('Index of Preference Change')+
        theme(
    # Remove panel border
    panel.border = element_blank(),  
    # Remove panel grid lines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # Remove panel background
    panel.background = element_blank(),
    # Add axis line
    axis.line = element_line(colour = "black",size=2),
    axis.ticks.length=unit(.25, "cm"))+
    theme(text = element_text(size=34))

```


```{r}
model_hueDistance<-lm(value~diff,allPairsTogether%>%dplyr::filter(class=='Fixed'))
sstable<-car::Anova(model_hueDistance, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_hueDistance)$fstatistic[1])
df_model_hueDistance <- unname(summary(model_hueDistance)$fstatistic[2])
df_res <- unname(summary(model_hueDistance)$fstatistic[3])
rsq <- summary(model_hueDistance)$r.squared
p <- pf(fstat, df_model_hueDistance, df_res, lower.tail = FALSE)
```

$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$. 

# Instability As a Function of Hue Rank
```{r, fig.width = 18, fig.asp = 0.5, fig.align = 'center', fig.cap=') Index of Preference Change as a function of the difference between the preference ranks between two hues.  This is generally a declining function regardless of the hues.  This decline again indicates that hues that have similar preferences and are thus harder to compare, yield more instability, regardless if they are neighbors in chromatic space.   '}
ggplot(allPairsTogether%>%dplyr::filter(class=='Fixed'),aes(x=OrankDiff,y=value, group=OrankDiff))+
  stat_summary(fun = "mean", geom = "point",size=3)+
  stat_summary(fun.data = "mean_se", geom = "errorbar",width=0.1,size=1)+
  xlab('Distance Between Hue Ranks')+ ylab('Index of Preference Change')+
        theme(
    # Remove panel border
    panel.border = element_blank(),  
    # Remove panel grid lines
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # Remove panel background
    panel.background = element_blank(),
    # Add axis line
    axis.line = element_line(colour = "black",size=2),    
    axis.ticks.length=unit(.25, "cm"))+
    theme(text = element_text(size=14))
```


# Relationship Between Valence and Instability 

```{r valence, fig.width = 18, fig.asp = 0.5, fig.align = 'center', fig.cap = 'The relationship between associaion valence and instability. Here, instability is defined as the mean change in the number of times a stimuli was picked, while the mean association valence is the average of the association valences a stimuli. The data is limited to cars and shirts only.'}

ggplot(allCountsSummary,
       aes(x=meanValence,
           y=fixed_diff,))+
        labs(x='Mean Association Valence Rating', y='Index of Preference Change')+
  stat_summary(fun = "mean", geom = "point",size=6)+
  stat_summary(fun.data = "mean_se", geom = "errorbar",size=2,width=0.1)+
                  theme(
              # Remove panel border
              panel.border = element_blank(),  
              # Remove panel grid lines
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              # Remove panel background
              panel.background = element_blank(),
              # Add axis line
              axis.line = element_line(colour = "black",size=2),
                  axis.ticks.length=unit(.25, "cm"))+
  scale_x_continuous(breaks= round(seq(min(allCountsSummary$meanValence),max(allCountsSummary$meanValence),by=1),1))+
   theme(text = element_text(size=24))
```


ANOVA 
```{r}
model_curve<-lm(fixed_diff~meanValence+meanValenceSqrd,allCountsSummary)
sstable<-car::Anova(model_curve, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_curve)$fstatistic[1])
df_model_curve <- unname(summary(model_curve)$fstatistic[2])
df_res <- unname(summary(model_curve)$fstatistic[3])
rsq <- summary(model_curve)$r.squared
p <- pf(fstat, df_model_curve, df_res, lower.tail = FALSE)
```

$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$.

Tukey
```{r}
TukeyHSD(aov(fixed_diff~as.factor(meanValence),allCountsSummary))
```

Compare Models
```{r}
model.1<-lm(fixed_diff~meanValence,allCountsSummary)
model.2<-lm(fixed_diff~meanValence+meanValenceSqrd,allCountsSummary)
compareLM(model.1, model.2)
anova(model.1,model.2)
```



# Gender Differences
```{r, fig.width = 10, fig.asp = 0.7, fig.align = 'center', fig.cap='Men are more unstable than women in their aesthetic preferences.'}
ggplot(allPairsDistance_AF,aes(Gender,Instability))+
  stat_summary(fun='mean',geom='point',size=2)+
  stat_summary(fun.data='mean_se',geom='errorbar',size=1,width=0.1)+
     labs(y=' Index of Preference Change',x='Gender ')+
      ggsignif::geom_signif(comparisons = list(c('Female','Male')),annotation=c("*"),map_signif_level = TRUE,y_position = c(.20),tip_length = 0.005)+
  
    coord_cartesian(ylim=c(0.175,0.25)) +
                theme(
              # Remove panel border
              panel.border = element_blank(),  
              # Remove panel grid lines
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              # Remove panel background
              panel.background = element_blank(),
              # Add axis line
              axis.line = element_line(colour = "black",size=2),
                  axis.ticks.length=unit(.25, "cm"))+
              theme(text = element_text(size=14))
```


# T test For Gender Differences

```{r, warning= FALSE}
genderTest<-t.test(Instability~Gender,allPairsDistance_AF)

tStat<-genderTest$statistic[['t']]
tDF<-genderTest$parameter[['df']]
tPval<-genderTest$p.value

genderTest
```




# Age Differences

```{r, fig.width = 12, fig.asp = 0.75, fig.align = 'center', fig.cap='Age groups between 19-29 are more unstable than the older age groups from 29-65.'}

ggplot(allPairsDistance_AF,
      aes(adaptiveCut,Instability))+
  stat_summary(fun='mean',geom='point',size=2)+
  stat_summary(fun.data='mean_se',geom='errorbar',width=0.1,size=1)+
   labs(y=' Index of Preference Change',x='Age Group')+
                theme(
              # Remove panel border
              panel.border = element_blank(),  
              # Remove panel grid lines
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              # Remove panel background
              panel.background = element_blank(),
              # Add axis line
              axis.line = element_line(colour = "black",size=2),
              axis.ticks.length=unit(.25, "cm"))+
    scale_x_discrete(labels=c('19-23','23-31','31-37','37-44','44-54','54-65'))+
  coord_cartesian(ylim = c(.15,.275))+
 theme(text = element_text(size=14))






```

ANOVA 
```{r}
model_adaptiveCut<-lm(Instability~adaptiveCut,allPairsDistance_AF)
sstable<-car::Anova(model_adaptiveCut, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_adaptiveCut)$fstatistic[1])
df_model_adaptiveCut <- unname(summary(model_adaptiveCut)$fstatistic[2])
df_res <- unname(summary(model_adaptiveCut)$fstatistic[3])
rsq <- summary(model_adaptiveCut)$r.squared
p <- pf(fstat, df_model_adaptiveCut, df_res, lower.tail = FALSE)
```
$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$

# Age and gender interaction
```{r}
model_adaptiveCutGender<-lm(Instability~adaptiveCut*Gender,allPairsDistance_AF)
sstable<-car::Anova(model_adaptiveCutGender, type=3)
sstable$pes <- c(sstable$'Sum Sq'[-nrow(sstable)], NA)/(sstable$'Sum Sq' + sstable$'Sum Sq'[nrow(sstable)]) # SS for each effect divided by the last SS (SS_residual)
# knitr::kable(sstable,digits=3)
options(knitr.kable.NA = '') # this will hide missing values in the kable table
colnames(sstable) <- c("SS", "df", "$F$", "$p$", "partial $\\eta^2$")

knitr::kable(sstable[-1, ], digits = 3, format = "pandoc", caption = "ANOVA table")

fstat <- unname(summary(model_adaptiveCutGender)$fstatistic[1])
df_model_adaptiveCutGender <- unname(summary(model_adaptiveCutGender)$fstatistic[2])
df_res <- unname(summary(model_adaptiveCutGender)$fstatistic[3])
rsq <- summary(model_adaptiveCutGender)$r.squared
p <- pf(fstat, df_model_adaptiveCutGender, df_res, lower.tail = FALSE)
```
$R^2$=`r round(rsq, 2)`, $F(`r round(df_model, 0)`, `r round(df_res, 0)`)=`r round(fstat, 2)`$, $p=`r ifelse(round(p, 3) == 0, "<.001", round(p, 3))`$

Tukey Post Hoc
```{r}
TukeyHSD(aov(Instability~adaptiveCut,allPairsDistance_AF))#sub is male 45yo
```

Pearson correlation vs Kendall correlation
```{r}
cor.test(allPairsDistance_AF$Age,allPairsDistance_AF$Instability)
cor.test(allPairsDistance_AF$Age,allPairsDistance_AF$Instability,method = 'kendall')
```


